Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-24 manuscript/ERL_global_C_review.Rmd
fill in full author names & affiliations

Becky Banbury Morgan

Ben Bond-Lamberty

@@

Abigail Ferson

Jennifer McGarvey

@@

Maria Wang

@@

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; National Zoological Park, Front Royal, VA 22630, USA
2. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama
3.
4.
5. The Nature Conservancy, Arlington VA 22203
6.

@@

\newpage
\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | C cycle diagram for young tropical broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 9 | C cycle diagram for young temperate broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 10 | C cycle diagram for young temperate conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 11 | C cycle diagram for young boreal conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

>>>>

Becky Banbury Morgan^3^

Ben Bond-Lamberty^4

@@

Abigail E. Ferson^1,6^

Jennifer C. McGarvey^1^

@@

Maria M. H. Wang^1,7^

@@

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; National Zoological Park, Front Royal, VA 22630, USA
2. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama
3. School of Geography, University of Leeds, Leeds, UK
4. Joint Global Change Research Institute, Pacific Northwest National Laboratory, College Park Maryland 20740, USA 
5. The Nature Conservancy; Arlington VA 22203, USA
6. College of Natural Resources, University of Idaho; Moscow, Idaho 83843, USA
7. Grantham Centre for Sustainable Futures and Department of Animal and Plant Sciences, University of Sheffield, Western Bank, Sheffield, South Yorkshire S10 2TN, UK

@@

\newpage
\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | C cycle diagram for young tropical broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 9 | C cycle diagram for young temperate broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 10 | C cycle diagram for young temperate conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 11 | C cycle diagram for young boreal conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}
